Towards Cloud Bursting for Extreme Scale Supercomputers

### 2014-06-27 paper/paper.tex
0627

%Multi-user can use supercomputer at the same by using batch queue system which manage nodes and job submission.
Although supercomputer can offer a high computational cpacity, there are some situations HPC system can not satisfy user's demands even there are still some idle nodes, consider there are 50 nodes available, a user submit a serial application use only one node for an hour, after that, a job using 50 nodes is submitted, and have to wait until previous job finished although there are 49 nodes remainning available.
%high parallel application runs faster on Supercomputer for fully usage of computing resource, but a serial application will occupy computing nodes for a long time causing other application must wait.
Another problem is the power problem in summer, in order to reduce power consumption, some nodes will be forced to be shut down, reducing numbers of nodes will make the first problem more serous.

@@

Throughput-based Model, Cost-based Model and buffer queue write back model will be described in this section.
Throughput-based Model compare one-side buffer throughput with two-side buffer, cost-based model compare one-side buffer cost with two-side buffer, and buffer queue write back model. 
We make definitions shows in Table.~\ref{definition} in order to describe our model:
\begin{table}[tb]
	\caption{Definition of parameters}
	\label{definition}
\begin{tabular}{|p{3cm}|p{5cm}|}
	\hline
	$c_1,c_2$&Numbers of computing nodes in system 1 and system 2\\\hline
	$n_1, n_2$&Numbers of I/O buffer nodes in system 1 and system 2.\\\hline
	$m_1,m_2$&Available memory size for each I/O node in system 1 and 2, also the maximum buffer size will be $n_1\times m_1$ and $n_2\times m_2$\\\hline
	$D_1(n_2),D_2(n_2)$&Throughput when $n_2$($n_1$) I/O nodes in system 1 (system 2) connect to storage in the other system directly, here we assume only I/O nodes in each system have Internet connection.\\\hline
	$I(n_1,n_2)$& 	Internet throughput using $n_1,n_2$ I/O buffer nodes respectively, Since overall Internet throughput is affected by number of nodes involved in connection.\\\hline
	$E_1(n_1), E_2(n_2)$&Interconnection network throughput in system 1 and 2, although interconnection throughput is also affected by numbers of I/O nodes and computing nodes, numbers of users will running application on different number of computing nodes.\\\hline
	%, it is difficult to compute each throughput, so here we use $E_1(n_1)$ to refer to limitation of maximum throughput of interconnection network in system 1 with $n_1$ I/O nodes, likely ,$E_2(n_2)$ is limitation of maximum throughput of interconnection network in system 2 with $n_2$ I/O nodes.
	$M_1(n_1),M_2(n_2)$& Throughput of connection between storage and $n_1$ I/O nodes in system 1 and storage and $n_2$ I/O nodes in system 2.\\\hline
	$C_1\_Money(T)$,$C_2\_Money(T)$& Cost for standard node in system 1 and 2 for $T$ time usage\\\hline
	%and cost for node in system 1 is $C_2\_Money(T)$ for $T$ time usage, and since I/O nodes may use a better network, 
	$C_1\_High\_Money(T)$,$C_2\_High\_Money(T)$& cost I/O nodes in system 1 and 2 for $T$ time usage, since I/O nodes may use a better network condition, we assume it will cost more than normal nodes.\\\hline
\end{tabular}
\end{table}

>>>>

%Multi-user can use supercomputer at the same by using batch queue system which manage nodes and job submission.
Although supercomputer can offer a high computational cpacity, there are some situations HPC system can not satisfy user's demands even there are still some idle nodes, consider there are 50 nodes available, a user submit a serial application use only one node for an hour, after that, a job using 50 nodes is submitted, and have to wait until previous job finished although there are 49 nodes remainning available.
%high parallel application runs faster on Supercomputer for fully usage of computing resource, but a serial application will occupy computing nodes for a long time causing other application must wait.
Another problem is the power problem in summer, in order to reduce power consumption, some nodes will be forced to be shut down (peak shift in TSUBAME\cite{TSUBAME}), reducing numbers of nodes will make the first problem more serous.

@@

Throughput-based Model, Cost-based Model and buffer queue write back model will be described in this section.
Throughput-based Model compare one-side buffer throughput with two-side buffer, cost-based model compare one-side buffer cost with two-side buffer, and buffer queue write back model. 
We make definitions shows in \tabref{definition} in order to describe our model:
\begin{table}[tb]
	\caption{Definition of parameters}
	\label{definition}
\begin{tabular}{|p{3cm}|p{5cm}|}
	\hline
	$c_1,c_2$&Numbers of computing nodes in system 1 and system 2\\\hline
	$n_1, n_2$&Numbers of I/O buffer nodes in system 1 and system 2.\\\hline
	$m_1,m_2$&Available memory size for each I/O node in system 1 and 2, also the maximum buffer size will be $n_1\times m_1$ and $n_2\times m_2$\\\hline
	$D_1(n_2),D_2(n_2)$&Throughput when $n_2$($n_1$) I/O nodes in system 1 (system 2) connect to storage in the other system directly, here we assume only I/O nodes in each system have Internet connection.\\\hline
	$I(n_1,n_2)$& 	Internet throughput using $n_1,n_2$ I/O buffer nodes respectively, Since overall Internet throughput is affected by number of nodes involved in connection.\\\hline
	$E_1(n_1), E_2(n_2)$&Interconnection network throughput in system 1 and 2, although interconnection throughput is also affected by numbers of I/O nodes and computing nodes, numbers of users will running application on different number of computing nodes.\\\hline
	%, it is difficult to compute each throughput, so here we use $E_1(n_1)$ to refer to limitation of maximum throughput of interconnection network in system 1 with $n_1$ I/O nodes, likely ,$E_2(n_2)$ is limitation of maximum throughput of interconnection network in system 2 with $n_2$ I/O nodes.
	$M_1(n_1),M_2(n_2)$& Throughput of connection between storage and $n_1$ I/O nodes in system 1 and storage and $n_2$ I/O nodes in system 2.\\\hline
	$C_1\_Money(T)$,$C_2\_Money(T)$& Cost for standard node in system 1 and 2 for $T$ time usage\\\hline
	%and cost for node in system 1 is $C_2\_Money(T)$ for $T$ time usage, and since I/O nodes may use a better network, 
	$C_1\_High\_Money(T)$,$C_2\_High\_Money(T)$& cost I/O nodes in system 1 and 2 for $T$ time usage, since I/O nodes may use a better network condition, we assume it will cost more than normal nodes.\\\hline
\end{tabular}
\end{table}
